Ethnicity sensitive author disambiguation using semi-supervised learning

### 2015-08-28 paper/paper.tex
save

\textit{Blocking.} The good precision of the baseline ($0.9901$), but its
lower recall ($0.9760$) suggest that the blocking strategy might be the
limiting factor to further overall improvements.
As shown in Table~\ref{table:blocking}, the maximum recall (\ie, if within a block, all signatures were clustered optimally) for SFI is $0.9828$.
At the price of fewer and therefore slightly larger blocks (as reported in the right column of Table~\ref{table:blocking}), the
proposed phonetic-based blocking strategies show better maximum recall (all
around $0.9905$), thereby pushing further the upper bound on the maximum
performance of author disambiguation.
As Table~\ref{table:results} shows, switching to either Double metaphone or NYSIIS phonetic-based blocking allows
to improve the overall F-measure score, trading precision for recall.
In particular, the NYSIIS-based phonetic blocking shows to be the most effective when applied
to the baseline (with an F-measure of $0.9850$) while also being the most
efficient computationally (with 10857 blocks versus 12978 for the baseline).

@@

Note that the maximum recalls of blocking strategies using phonetization are
raised also due to the better handling of multiple given names cases described in Section \ref{methods:blocking}.

>>>>

\textit{Blocking.} The good precision of the baseline ($0.9901$), but its
lower recall ($0.9760$) suggest that the blocking strategy might be the
limiting factor to further overall improvements.
As shown in Table~\ref{table:blocking}, the maximum recall (\ie, if within a block, all signatures were clustered optimally) for SFI is $0.9828$.
At the price of fewer and therefore slightly larger blocks (as reported in the right column of Table~\ref{table:blocking}), the
proposed phonetic-based blocking strategies show better maximum recall (all
around $0.9905$), thereby pushing further the upper bound on the maximum
performance of author disambiguation.
Let us remind however that the reported maximum recalls for the blocking strategies using phonetization are
also raised due to the better handling of multiple surnames, as described in Section \ref{methods:blocking}.

As Table~\ref{table:results} shows, switching to either Double metaphone or NYSIIS phonetic-based blocking allows
to improve the overall F-measure score, trading precision for recall.
In particular, the NYSIIS-based phonetic blocking shows to be the most effective when applied
to the baseline (with an F-measure of $0.9850$) while also being the most
efficient computationally (with 10857 blocks versus 12978 for the baseline).

@@
